### 2020-01-22 reports/article.tex
[ci skip] corrected abstract to match word limit

  \emph{Methods} For each urban agglomeration, four temporal snapshots from 1980 to 2016 have been derived from the land use inventory of the Swiss Federal Statistical Office.
  % A combination of landscape metrics, urban growth modes and fractal analysis serves to characterize the spatiotemporal patterns of urbanization.
  By making use of fractal analysis to study the area-radius relationship of urban land, each urban agglomeration is separated into two characteristic urban extents according to the distance of the city center, namely the inner and outer zones. The landscape metrics and growth modes are then computed at such extents. % and used to validate the diffusion and coalescence

  \emph{Results} % The fractal analysis of the area-radius relationship
  The time series of landscape metrics and growth modes reveal fairly different patterns when computed in the inner and outer zones respectively. Bern and Lausanne exhibit mostly traits of coalescence stages at the inner zone while displaying many characteristics of diffusion in the outer zone.
  % By contrast, Zurich, which is significantly more urbanized at higher distances to the city center and, shows
  In contrast, the trends of observed in the inner and outer zones of Zurich are both reminiscent of a coalescence of urban patches.

  \emph{Conclusions} Fractal analysis of the area-radius relationship can be a useful approach to detect characteristic extents of urban agglomerations at which distinct spatiotemporal patterns might be observed. Current models of urbanization patterns should incorporate the notion of characteristic extents more explicitly.

>>>>

  \emph{Methods} % For each urban agglomeration, four temporal snapshots from 1980 to 2016 have been derived from the land use inventory of the Swiss Federal Statistical Office.
  % A combination of landscape metrics, urban growth modes and fractal analysis serves to characterize the spatiotemporal patterns of urbanization.
  % By making use of fractal analysis to study the area-radius relationship of urban land, each urban agglomeration is separated into two characteristic urban extents according to the distance of the city center, namely the inner and outer zones. The landscape metrics and growth modes are then computed at such extents. % and used to validate the diffusion and coalescence
  For each urban agglomeration, four temporal snapshots from 1980 to 2016 have been derived from the land use inventory of the Swiss Federal Statistical Office. Fractal analysis of the area-radius relationship of urban land is used to separate each agglomeration into two characteristic spatial extents according to the distance of the city center, namely the inner and outer zones. The landscape metrics and growth modes are then computed at such extents.

  \emph{Results} % The fractal analysis of the area-radius relationship
  % The time series of landscape metrics and growth modes reveal fairly different patterns when computed in the inner and outer zones respectively. Bern and Lausanne exhibit mostly traits of coalescence stages at the inner zone while displaying many characteristics of diffusion in the outer zone.
  % By contrast, Zurich, which is significantly more urbanized at higher distances to the city center and, shows
  % In contrast, the trends of observed in the inner and outer zones of Zurich are both reminiscent of a coalescence of urban patches.
  The time series of landscape metrics and growth modes reveal fairly different patterns when computed in the inner and outer zones respectively. Bern and Lausanne exhibit mostly traits of coalescence stages at the inner zone while displaying many characteristics of diffusion in the outer zone. In contrast, the trends of observed in the inner and outer zones of Zurich are both reminiscent of a coalescence stages.

  \emph{Conclusions} % Fractal analysis of the area-radius relationship can be a useful approach to detect characteristic extents of urban agglomerations at which distinct spatiotemporal patterns might be observed. Current models of urbanization patterns should incorporate the notion of characteristic extents more explicitly.
  Fractal analysis can be a useful approach to detect characteristic extents of urban agglomerations at which distinct spatiotemporal patterns might be observed. Current models of urbanization patterns should incorporate the notion of characteristic extents more explicitly.
